\begin{thebibliography}{1}
		\bibliographystyle{ieeetr} 
		\footnotesize
		
		\bibitem{1}
		Teng, Fan, and Qingwei Zhang. "Empirical Analysis on Interest-Rate Risk to Chinese Life Insurers and Scenario Testing." In 2011 International Conference on Management and Service Science, pp. 1-3. IEEE, 2011.

		
		\bibitem{2}
		Vaswani, Ashish, Noam Shazeer, Niki Parmar, Jakob Uszkoreit, Llion Jones, Aidan N. Gomez, Łukasz Kaiser, and Illia Polosukhin. "Attention is all you need." In Advances in neural information processing systems, pp. 5998-6008. 2017.

		
		\bibitem{3}
		 Gülpinar, Nalan, and Dessislava Pachamanova. "A robust optimization approach to asset-liability management under time-varying investment opportunities." Journal of Banking \& Finance 37, no. 6 (2013): 2031-2041.
		
		\bibitem{4}
		Li, Hongxi, and Guotai Chi. "Assets and Liabilities Portfolio Optimal Model based on ES Controlled Interest Rate Risk." In Proceedings of the International Conference on Business and Information Management, pp. 1-5. ACM, 2017.
		
		
		\bibitem{5} 
		Images are drawn in a software package called \emph{Jupyter Notebook}.
		
		\bibitem{6}
		 Qin, Yao, Dongjin Song, Haifeng Chen, Wei Cheng, Guofei Jiang, and Garrison Cottrell. "A dual-stage attention-based recurrent neural network for time series prediction." arXiv preprint arXiv:1704.02971 (2017).
		
		\bibitem{7}
		 Liu, Jian, Yubo Chen, Kang Liu, and Jun Zhao. "Attention-Based Event Relevance Model for Stock Price Movement Prediction." In China Conference on Knowledge Graph and Semantic Computing, pp. 37-49. Springer, Singapore, 2017.
		  
		 \bibitem{8}
		 Li, Hao, Yanyan Shen, and Yanmin Zhu. "Stock Price Prediction Using Attention-based Multi-Input LSTM." In Asian Conference on Machine Learning, pp. 454-469. 2018.

		\bibitem{9}
		Liu, Huicheng. "Leveraging Financial News for Stock Trend Prediction with Attention-Based Recurrent Neural Network." arXiv preprint arXiv:1811.06173 (2018).
		
		\bibitem{10}
		\url{https://colab.research.google.com} (A cloud based data science work space similar to jupyter notebook).
		 
		 \bibitem{11}
		  https://www.rbi.org.in/scripts/NotificationUser.aspx?Id=16\&Mode=0
		 
		 \bibitem{12}
		 Images are drawn in a software package called \emph{RStudio} and \emph{Jupyter Notebook}.		 
		 
		 \bibitem{13}
		 Goodfellow, Ian, Yoshua Bengio, and Aaron Courville. Deep learning. MIT press, 2016.
		 
		 \bibitem{14}		 
		 \url{https://www.tensorflow.org/} (Helpful documentation for learning tensorflow, a software library used to design, develop and train deep learning models.)
		 
		 \bibitem{15}
		 \url{https://keras.io/} (For creating deep learning model on top of tensoeflow.)
		 
		 \bibitem{16}
		 Mounika, P.; Sastry, V.N., “Cash-flow optimization models for asset liability management” (M-tech project report, IDRBT), 2011.

		 
		 \bibitem{17}
		 Chaudhury, Rahul; Sastry, V.N., “Fuzzy optimization based asset liability management” (M-Tech project report, IDRBT), 2014.

		 
		 \bibitem{18}
		 Shumway, Robert H., and David S. Stoffer. Time series analysis and its applications: with R examples. Springer, 2017.	
		 
		 \bibitem{19}
		 \url{https://data.world/lpetrocelli/czech-financial-dataset-real-anonymized-transactions/workspace/data-dictionary} (Source of dataset used in Chapter 2).
		 
		
		

		
		 
		
\end{thebibliography}
